Algomusicology, ???, Profit

### 2016-04-02 paper.tex
A listing of a set is an enumeration.

The Kleene star is the set of all possible strings built from a set of elements.

@@

We can use this construction with an ASCII alphabet to obtain all possible ASCII strings as a lazy
sequence. This results in something very similar to the Library of Babel as imagined by Jorge Luis Borges. In his
vast fictional library, thousands of hexagonal rooms house all possible books of four hundred and ten pages.

>>>>

The Kleene star is the set of all possible strings built from a set of elements. Here is a function that takes a set of
elements and produces an enumeration of the Kleene star of the set as a lazy sequence.

@@

We can use this construction with an ASCII alphabet to obtain all possible ASCII strings.
This results in something very similar to the Library of Babel as imagined by Jorge Luis Borges. In his
vast fictional library, thousands of hexagonal rooms house all possible books of four hundred and ten pages.
